---
title: "Answers to JDPers' R Questions"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Disclaimer

R is an open-source project. Anyone can contribute to its codebase, which makes it possible to use multiple ways to achieve a certain purpose. In programmers way, we call it **There's more than one way to do it (TMTOWTDI)**. (https://en.wikipedia.org/wiki/There%27s_more_than_one_way_to_do_it) Sometimes, they bring us the exactly same results. Sometimes not. I'll try not to list all of them here, but if it is well-known that there's a noticeable differences between meathods, I'll let you know.

## Introduction

This document is for UCSD/SDSU JDPers. Anybody can edit the answers.

```{r}
print("hello JDPers")
plot(sin(seq(0, 10, by=0.1)), type = 'l')
```

## Package Installation and Loading

There are a few ways to install & load packages. This is the easiest way.

* Install a ***pacman*** package, if it is not installed in your computer. This is a one-time thing. If you have done it before, you don't have to do it again. 
```{r}
if ("pacman" %in% rownames(installed.packages()) == FALSE) {
  install.packages("pacman")
}

```

* From now on, you don't have to do the ***"if"*** things above for the package installation ever. Use this:

```{r}
pacman::p_load(tidyverse, readxl, writexl)
```



## File Read

Before we proceed to file reading, we need sample data files.


### [FYI] Sample File Generation

This is only for sample data generation. You don't have to get it now.

```{r}
c1 <- c(1,2,3,4,5)
c2 <- c(2,3,4,5,6)
c3 <- c(3,4,5,6,7)
dt1 <- data.frame(c1=c1, c2=c2, c3=c3)
rm(list=c("c1", "c2", "c3"))

# save it to csv
write.csv(x = dt1, file = "test.csv")

# save it to xlsx format
pacman::p_load(writexl)
write_xlsx(x = dt1, path = "test.xlsx")


# save it to Rdata format (THIS IS FASTEST!!)
save(dt1, file = "test.Rdata")
```

### CSV File read

You can read CSV files with ***read.csv*** function.

```{r}
dt2 <- read.csv("test.csv")
dt2
```

### Read XLSX file

You can read XLSX files with ***read_xlsx*** function in readxl library.

```{r}
pacman::p_load(readxl)

dt3 <- read_excel(path = "test.xlsx")
dt3
```

### Read .Rdata file (Fastest)

.RData file is a raw data type specifically designed for R. Thus, it is fastest way to save or load the R data object.

It has a single serious downside. You can't change the variable name when you load it up. It automatically loads the data object under exactly same variable name. Let's try it here.

```{r}
# get the list of current variables
list_of_variable = ls()
list_of_variable

if ("dt1" %in% list_of_variable) {
  print("We already has the dt1 variable. I'm going to delete it.")
  rm(dt1)
} else {
  print("We don't have the dt1 variable. Let's proceed.")
}

# let's get the list of variables again
list_of_variable = ls()
list_of_variable

print("We can see there's no dt1 variable")

# let's load the RData file
load("test.Rdata")


# let's get the list of variables again
list_of_variable = ls()
list_of_variable

print("We can see we have dt1 variable again")

```


